Optimizing Large Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2011-11-29 paper/self_calibration_I.tex
euclid: add Wittman reference, kind of...
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@19959 03a3cea6-2c03-0410-ac9b-9271b1c66c29

\section{Self-Calibrating the Survey-Wide Dataset}
\label{sec:self_cal}
We self-calibrate the dataset generated in the survey simulations to recover a best possible estimate of the true instrument response applied and the true source fluxes. This self-calibration procedure has been successfully applied to ground-based imaging surveys, such as the Sloan Digital Sky Survey \citep{pad08}\footnote{Here this procedure is dubbed ``uber-calibration.''}. This iterative procedure comprises two steps: (1) a refinement of the source flux estimates based on the latest instrument response model and (2) a refinement of the instrument response model based on the updated source flux estimates. These steps are iterated until the system converges, or until it is clear that the system will not converge. There is a degeneracy in the problem, as both the true instrument response and the true source magnitudes are unknown. It is therefore only possible to calibrate the \textit{relative} instrument response and the \textit{relative} source fluxes. It is not possible to know, for example, if the sources are all fainter or if the instrument response is uniformly lower. In practice, this degeneracy can be broken through observations of a small number of standard absolute sources.

@@

\begin{thebibliography}{}
\bibitem[Padmanabhan et al. (2008)]{pad08} {Padmanabhan, N. et al., An Improved Photometric Calibration of the Sloan Digital Sky Survey Imaging Data, 2008, \apj~674, p1217.}
\bibitem[Windhorst et al. (2011)]{win11}{Windhorst, R.~A. et al., The Hubble Space Telescope Wide Field Camera 3 Early Release Science Data: Panchromatic Faint Object Counts for 0.2-2 $\upmu$m Wavelength, 2011, \apjs~193, p27.}
\end{thebibliography}
\clearpage

>>>>

\section{Self-Calibrating the Survey-Wide Dataset}
\label{sec:self_cal}
We self-calibrate the dataset generated in the survey simulations to recover a best possible estimate of the true instrument response applied and the true source fluxes. This self-calibration procedure has been successfully applied to ground-based imaging surveys, such as the Sloan Digital Sky Survey \citep{pad08}\footnote{Here this procedure is dubbed ``uber-calibration.''} and the Deep Lens Survey \citep{wit11}. This iterative procedure comprises two steps: (1) a refinement of the source flux estimates based on the latest instrument response model and (2) a refinement of the instrument response model based on the updated source flux estimates. These steps are iterated until the system converges, or until it is clear that the system will not converge. There is a degeneracy in the problem, as both the true instrument response and the true source magnitudes are unknown. It is therefore only possible to calibrate the \textit{relative} instrument response and the \textit{relative} source fluxes. It is not possible to know, for example, if the sources are all fainter or if the instrument response is uniformly lower. In practice, this degeneracy can be broken through observations of a small number of standard absolute sources.

@@

\begin{thebibliography}{}
\bibitem[Padmanabhan et al. (2008)]{pad08} {Padmanabhan, N. et al., An Improved Photometric Calibration of the Sloan Digital Sky Survey Imaging Data, 2008, \apj~674, p1217.}
\bibitem[Windhorst et al. (2011)]{win11}{Windhorst, R.~A. et al., The Hubble Space Telescope Wide Field Camera 3 Early Release Science Data: Panchromatic Faint Object Counts for 0.2-2 $\upmu$m Wavelength, 2011, \apjs~193, p27.}
\bibitem[Wittman et al. (2011)]{wit11}{XX}
\end{thebibliography}
\clearpage
